Conformance Checking Using Embeddings and their Applicability in the Internet of Things

### 2021-12-15 paper.tex
Added algorithms

% !TeX spellcheck = en_GB
% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{template/llncs}
%
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage[autostyle]{csquotes}  
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{caption}
\usepackage{subcaption}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

In the last two decades, the cost for networking components has decreased significantly and a growing number of microcontrollers, embedded systems, and electronic devices now have some form of networking ability.
This increasing networked structure that enables easy information sharing between the members of the network has become known under a few names, most prominently as the "Internet of Things".
Unfortunately due to shifting developments in the last two decades and marketing efforts associated with the Internet of Things, it is hard to pin down the exact meaning of the term. 
The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} on the topic:
\blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  interoperable information and communication technologies.}

@@

\section{Background}
\subsection{Conformance Checking}
Conformance checking covers a range of different methods that aim to quantify how well an event log (or even just a single trace) and a process model fit together.
Our intuitive expectation would be that a model that allows for exactly those traces contained in the event log would conform perfectly, whereas a model that allows for none of the traces seen in the log would have very low conformance.
The aim of conformance checking is the formalization of this imprecise intuitive understanding of fitting together and the development of methods and algorithms that can accurately quantify precisely this intuition.

\subsubsection{Uses}
The uses of such an approach can generally be divided into two relatively distinct subcategories, depending on whether the event log or the process model are seen as normative.
If the process model is considered normative, conformance checking allows for the detection of deviations, i.e. observed traces that are not possible according to the model.
From such information a number of useful analyses can follow, e.g. where do deviations happen, which resources are involved in deviations, and how exactly these traces deviate from the model.
It should be pointed out that the word "deviation" is negatively connotated in English, however, for the purpose of process intelligence it should be viewed as a neutral category. 
For example, an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, based on which refinements to the process model could be made.
An example of negative conclusions may be the detections of deviations that do not follow proper legal or procedural requirements of the process, such as requiring two different persons to review an important document before signing off on it. In such a case knowledge of these deviations is required to ensure proper execution of the process.

@@

\subsection{Natural Language Processing}

As laid out in the previous section, both classical branches of conformance checking exhibit major drawbacks.
Besides approaches aiming to ameliorate certain disadvantages of such methods, there has also been a growing interest in applying novel techniques from other fields to the problem of conformance checking.
One such proposal is the application of techniques from the area of natural language processing for conformance checking as discussed in \cite{PBWe20}.

@@

\section{Method}

Many conformance checking algorithms, notably the classical ones outlined above, aim to measure conformance between a log and a model.
While this is the fundamental question to be answered, this comparison between two different types of objects greatly complicates the task.
However, by re-framing the problem one can greatly simplify it.
Instead of formulating the problem in terms of model-to-log comparison, one can formulate it as a comparison problem of a real log to a model log.
Such a reformulation of the problem is possible since all (reasonably defined) models are able to generate sample traces, and can therefore produce a model log.
Then the whole problem is reframed as log-to-log comparisons, i.e. determining similarities between objects of the same type, for which a broad range of techniques already exist.
This has the additional advantage that it is model-independent since no limitations apart from the ability to generate traces are put on the type of model.
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/structure}
	\caption{The general structure of the approach}
	\label{fig:structure}
\end{figure}

@@

\color{blue}
The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
This family of metrics has proved itself to be quite robust as well as accurate in the past.
The Earth Mover's distance measures the distance between two probability distributions.
The informal interpretation of this is that there are two distributions, represented by piles of earth.
The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
Clearly, the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.

@@

\subsubsection{Iterative Constrained Transfers}
The EMD and variants of it are very attractive since they are both very general and exhibit good accuracy for both search and classification.
A major drawback of such methods however is the cubic complexity in the size of the input distributions, which makes it infeasible for larger problems.
In the case of conformance checking the size of the input, distribution is determined by the number of activities in the log, for which good scalability is desired.
There are a number of techniques that aim to reduce the complexity of EMD-based approaches, that obtain an approximation of the EMD by relaxing some of the constraints.  
One example of such a method is the Relaxed Word Mover's distance which drops the second (inflow) constraint, thus greatly simplifying the solution.
While this makes it easier to calculate the solution, the RWMD only gives a lower bound on the WMD.
Another such method is the Iterative Constrained Transfers \cite{AtMi18} algorithm that has linear complexity in the size of the input distribution.
Instead of just dropping the inflow constraint it is instead replaced by an edge capacity constraint.
The main benefit of this is that it avoids the formulation as a linear program and is instead solvable using a much less powerful, but much quicker, direct algorithm.

@@

\section{Results}

\subsection{Experimental setup}

@@

\color{black}
\section{Discussion}

\todo{Proper fitness metric}

Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
Arguably the biggest limitation is the logs used for the experimental validation.
All used logs were completely synthetic, generated from random process trees.
It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases, and also to systematically broaden the parameters for random process tree generation to cover more different classes.

\color{blue}
It is also a  prerequisite for further research and possible usage of such methods to convert the distance metrics obtained into proper conformance metrics, especially by restricting values to the interval $[0,1]$.
When that is done further quantitative comparisons between the updated methods and established conformance checking techniques should be performed.
Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
A thorough investigation into the effect of these parameters should follow since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
Special attention should be placed on those cases for which the NLP techniques produced perfect values, whereas the others did not.
The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of the model spectrum and not misclassify nearly optimal models as perfect.
\color{black}
Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an orderless bag of words.
At least from an intuitive understanding of conformance checking order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
The authors themselves suggest considering the use of $n$-grams instead of 1-grams, since their application seems more feasible in business processes as compared to classical NLP.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{template/splncs04}
\bibliography{literature/bibliography}
%
\end{document}

>>>>

% !TeX spellcheck = en_US
% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{template/llncs}
%
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage[autostyle]{csquotes}  
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

In the last two decades, the cost for networking components has decreased significantly and a growing number of microcontrollers, embedded systems, and electronic devices now have some form of networking ability.
This increasing networked structure that enables easy information sharing between the members of the network has become known under a few names, most prominently as the "Internet of Things".
Unfortunately due to shifting developments in the last two decades and marketing efforts associated with the Internet of Things, it is hard to pin down the exact meaning of the term. 
The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} on the topic:
\blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  inter-operable information and communication technologies.}

@@

\color{green}
The following paper is structured as follows.
First some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
This includes a deeper look the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
Furthermore the important limitations of these two approaches are highlighted.
Then a brief overview over the required NLP techniques is given in \cref{sub:nlp}.
Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
After the techniques have been outlined a discussion of the results from their experiments follows in \cref{sec:results}.
\cref{sec:discussion} concludes the paper with a consideration of limitations in their approach and possible future work, as well as a discussion of the applicability of these techniques in the Internet of Things.
\color{black}

\section{Background}
\label{sec:background}
\color{green}
Naturally there are numerous sub problems to be solved in business process management.
Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in dependent problems.
For example the first step in many business process management use cases will be the discovery of a process model.
Once a process model has been obtained through some means further analyses can follow.
One of these fields is conformance checking, which as a technique, closely follows discovery, since it's main goal is to quantify how well a model conforms to a log.
There are currently two dominant branches of conformance checking, replay based algorithms and trace alignment algorithms.
Peeperkorn et al. present a novel conformance checking technique that follows and alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
However, before this technique can be discussed in depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing. 
\color{black}

\subsection{Conformance Checking}
\label{sub:conformance}
Conformance checking covers a range of different methods that aim to quantify how well an event log (or even just a single trace) and a process model fit together.
Our intuitive expectation would be that a model that allows for exactly those traces contained in the event log would conform perfectly, whereas a model that allows for none of the traces seen in the log would have very low conformance.
The aim of conformance checking is the formalization of this imprecise intuitive understanding of fitting together and the development of methods and algorithms that can accurately quantify precisely this intuition.
\subsubsection{Uses}
The uses of such an approach can generally be divided into two relatively distinct subcategories, depending on whether the event log or the process model are seen as normative.
If the process model is considered normative, conformance checking allows for the detection of deviations, i.e. observed traces that are not possible according to the model.
From such information a number of useful analyses can follow, e.g. where do deviations happen, which resources are involved in deviations, and how exactly these traces deviate from the model.
It should be pointed out that the word "deviation" is negatively connotated in English, however, for the purpose of process intelligence it should be viewed as a neutral category. 
For example, an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, based on which refinements to the process model could be made.
An example of negative conclusions may be the detection of deviations that do not follow proper legal or procedural requirements of the process, such as requiring two different persons to review an important document before signing off on it. In such a case knowledge of these deviations is required to ensure proper execution of the process.

@@

\subsection{Natural Language Processing}
\label{sub:nlp}
As laid out in the previous section, both classical branches of conformance checking exhibit major drawbacks.
Besides approaches aiming to ameliorate certain disadvantages of such methods, there has also been a growing interest in applying novel techniques from other fields to the problem of conformance checking.
One such proposal is the application of techniques from the area of natural language processing for conformance checking as discussed in \cite{PBWe20}.

@@

\section{Method}
\label{sec:method}
Many conformance checking algorithms, notably the classical ones outlined above, aim to measure conformance between a log and a model.
While this is the fundamental question to be answered, this comparison between two different types of objects greatly complicates the task.
However, by re-framing the problem one can greatly simplify it.
Instead of formulating the problem in terms of model-to-log comparison, one can formulate it as a comparison problem of a real log to a model log.
Such a reformulation of the problem is possible since all (reasonably defined) models are able to generate sample traces, and can therefore produce a model log.
Then the whole problem is re-framed as log-to-log comparisons, i.e. determining similarities between objects of the same type, for which a broad range of techniques already exist.
This has the additional advantage that it is model-independent since no limitations apart from the ability to generate traces are put on the type of model.
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/structure}
	\caption{The general structure of the approach}
	\label{fig:structure}
\end{figure}

@@

\color{blue}
\begin{algorithm}
	\caption{Word Mover's distance}\label{alg:wmd}
	\begin{algorithmic}
		\State $n:=$ vocabulary size
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\Function{$F_{WMD}$}{$p,q,c$}
			\State distance $\gets$ $\min \sum_{i,j=1}^n T_{ij}c(i,j)$
			\State subject to:
			\State $\sum_{j=1}^{n}T_{ij}=p_i \forall i \in \{1,...,n\}$ \Comment{Outflow}
			\State $\sum_{i=1}^{n}T_{ij}=q_j \forall j \in \{1,...,n\}$ \Comment{Inflow}
			\Return distance
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
This family of metrics has proved itself to be quite robust as well as accurate in the past.
The Earth Mover's distance measures the distance between two probability distributions.
The informal interpretation of this is that there are two distributions, represented by piles of earth.
The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
Clearly, the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.

@@

\subsubsection{Iterative Constrained Transfers}
\begin{algorithm}
	\caption{ACT}\label{alg:act}
	\begin{algorithmic}
		\State $k:=$ number of edges considered per activity
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\State $h_p,h_q :=$ amount of different activities in trace $p$ and trace $q$ 
		\Function{$F_{ICT}$}{$p,q,c,k$}
		\For{$i=1...h_p$}
			\State $s \gets \arg \min_k(c(i,[1,...,h_q]))$ \Comment{Find $k$ activities with the smallest cost}
			\While{$l < k$}
				\State $r \gets \min(p_i,q_{s(l)}))$ \Comment{Edge constraint, move as much as possible but no more than allowed}
				\State $p_i \gets p_i - r$ \Comment{Move weight}
				\State $t \gets t + rc(i,j)$ \Comment{Update cost}
				\State $l \gets l+1$
			\EndWhile
			\If{$p_i \neq 0$} \Comment{Move any remaining weight in $p_i$ to $q_{s(k)}$}
				$t \gets t + p_ic(i,s(k))$ \Comment{Move rest to $q_{s(k)}$}
			\EndIf
		\EndFor
		\Return $t$
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The EMD and variants of it are very attractive since they are both very general and exhibit good accuracy for both search and classification.
A major drawback of such methods however is the cubic complexity in the size of the input distributions, which makes it infeasible for larger problems.
In the case of conformance checking the size of the input, distribution is determined by the number of activities in the log, for which good scalability is desired.
There are a number of techniques that aim to reduce the complexity of EMD-based approaches, that obtain an approximation of the EMD by relaxing some of the constraints.  
One example of such a method is the Relaxed Word Mover's distance which drops the second (inflow) constraint, thus greatly simplifying the solution.
While this makes it easier to calculate the solution, the RWMD only gives a lower bound on the WMD.
Another such method is the Iterative Constrained Transfers \cite{AtMi18} algorithm that has linear complexity in the size of the input distribution.
Instead of just dropping the inflow constraint it is instead replaced by an edge capacity constraint.
The main benefit of this is that it avoids the formulation as a linear program and is instead solvable using a much less powerful, but much quicker, direct algorithm.

@@

\section{Results}
\label{sec:results}
\subsection{Experimental setup}

@@

\color{black}
\section{Discussion}
\label{sec:discussion}
\subsection{Future Work}
Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
Arguably the biggest limitation is the logs used for the experimental validation.
All used logs were completely synthetic, generated from random process trees.
It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases, and also to systematically broaden the parameters for random process tree generation to cover more different classes.

\color{blue}
It is also a  prerequisite for further research and possible usage of such methods to convert the distance metrics obtained into proper conformance metrics, especially by restricting values to the interval $[0,1]$.
When that is done further quantitative comparisons between the updated methods and established conformance checking techniques should be performed.
Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
A thorough investigation into the effect of these parameters should follow since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
Special attention should be placed on those cases for which the NLP techniques produced perfect values, whereas the others did not.
The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of the model spectrum and not misclassify nearly optimal models as perfect.
\color{black}
Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an order-less bag of words.
At least from an intuitive understanding of conformance checking order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
The authors themselves suggest considering the use of $n$-grams instead of 1-grams, since their application seems more feasible in business processes as compared to classical NLP.

@@

\color{green}
\subsection{Internet of Things}
An important question that was not yet properly addressed is whether this method offers benefits in the sue case of the internet of things and how well it would be adaptable to such an environment.
\color{black}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{template/splncs04}
\bibliography{literature/bibliography}
%
\end{document}
